\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-01-29 manuscript/manuscript.tex
fixed summary
did some bib cleaning

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows.
\jy{Whrere is the 'block' part?}
\begin{enumerate}
\item
  Draw a random sample $X^{(b)}_1,...,X^{(b)}_n$ from the empirical
  distribution~$F_n$.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $T^{(b)}_n$ to approximate the null distribution of the observed
  statistic. 
\end{enumerate}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr}
  \caption{A plot of the rejection rates as a function of $\tau$ for
 $n \in \{100, 200, 400, 800\}$ and marginal distribution 
 $\in \{N(8,8), \gamma(8,1)\}$.}
  \label{fig:rr}
\end{figure}

From 
Table~\ref{fig:rr}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

>>>>

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows.
\jy{Whrere is the 'block' part?}
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $T^{(b)}_n$ to approximate the null distribution of the observed
  statistic. 
\end{enumerate}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr}
  \caption{A plot of the rejection rates as a function of $\tau$ for
 $n \in \{100, 200, 400, 800\}$ and marginal distribution 
 $\in \{N(8,8), \Gamma(8,1)\}$.}
  \label{fig:rr}
\end{figure}

From 
Table~\ref{fig:rr}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\Gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.
